% 黒魔術
\expandafter\ifx\csname ifdraft\endcsname\relax
    \documentclass[a4paper,twoside,12pt,papersize, dvipdfmx]{iirthesis}
    \usepackage{amsmath,amssymb,amsthm}
    \usepackage{graphicx}
    \usepackage{subcaption}
    \usepackage{url}
    \usepackage{otf}
    \usepackage{minitoc}
    \usepackage{bm}
    \usepackage{amsmath,amssymb}
    \usepackage{times} % times new roman
    \begin{document}
    % ﾍﾞﾝﾘﾀﾞﾅｰ
    \newcommand{\figref}[1]{\figurename\ref{#1}}
    \newcommand{\tabref}[1]{\tablename\ref{#1}}
    \renewcommand{\eqref}[1]{式~(\ref{#1})}
    \newcommand{\chapref}[1]{\ref{#1}章}
    \newcommand{\secref}[1]{\ref{#1}節}
    \newcommand{\ssecref}[1]{\ref{#1}項}
    \newcommand{\appref}[1]{付録\ref{#1}}
\fi

\chapter{参考文献}\label{chap:bibliography}

\begin{thebibliography}{}
%1-intro
\bibitem[Dwivedi+ 2018]{dwivedi2018}
A. Dwivedi, Y. Kwon, A. J. McDaid, M. Liarokapis:
``EMG Based Decoding of Object Motion in Dexterous, In-Hand Manipulation Tasks,''
{\it 2018 7th IEEE International Conference on Biomedical Robotics and Biomechatronics (Biorob)},
2018, pp.~1025--1031, doi:~10.1109/BIOROB.2018.8487222.

\bibitem[Rimon+ 1999]{rimon1999} 
E. Rimon, A. Blake:
``Caging Planar Bodies by One-Parameter Two-Fingered Gripping Systems,''
{\it The International Journal of Robotics Research}, Vol.~18, no.~3, pp.~299--318, 1999.

\bibitem[込山 2021]{komiyama2021}
込山 隼:
``センサレスin-hand ケージングマニピュレーションによる物体の位置・姿勢制御'',
横浜国立大学大学院理工学府 機械・材料海洋系工学専攻, ポートフォリオ, 2021.
  
\bibitem[Hertkorn+ 2013]{hertkorn2013}
K. Hertkorn, M. A. Roa, C. Borst,
``Planning In-hand Object Manipulation with Multifingered Hands Considering Task Constraints'',
{\it Proceeding of the IEEE International Conference on Robotics and Automation}, 
pp.~617--624, 2013.

  \bibitem[Bircher+ 2019]{bircher2019}
      %Walter G. Bircher, Andrew S. Morgan, Kaiyu Hang, Aaron M. Dollar,
	W. G. Bircher, A. S. Morgan, K. Hang, A. M. Dollar,
  	``Energy Gradient-Based Graphs for Planning Within-Hand Caging Manipulation'',
  	{\it 2019 International Conference on Robotics and Automation (ICRA)},
  	pp.~2462--2467
  	2019.
    
      \bibitem[Chavan-Dafle+ 2020]{chavan-dafle2020}
 % 	Nikhil Chavan-Dafle, Rachel Holladay, Alberto Rodriguez,
 	N. Chavan-Dafle, R. Holladay, A. Rodriguez,
  	``Planar In-Hand Manipulation Via Motion Cones'',
  	 {\it The International Journal of Robotics Research},
  	 Vol.~39, No.~2--3, pp.~163--182,
  	2020.
  	
    \bibitem[Ospina+ 2020]{ospina2020}
%  	Diego Ospina, Alejandro Ramirez-Serrano,
	D. Ospina, A. Ramirez-Serrano,
  	``Sensorless In-Hand Manipulation by An Underactuated Robot Hand'',
  	 {\it ASME. J. Mechanisms Robotics. October 2020},
  	 Vol.~12, No.~5: 051009, 
  	2020.

    \bibitem[田原 2013]{tahara2013}
	田原 健二，
  	``動的安定把持に基づくマニピュレーション'',
  	 日本ロボット学会誌,
  	 Vol.~31, No.~4, pp.~364--369,
  	2013.  	

    \bibitem[田原 2020]{tahara2020}
    	田原 健二，
  	``多指ロボットハンドによる物体把持のダイナミクスと受動性'',
  	 システム/情報/制御,
  	 Vol.~64, No.~12,pp.~477--482,
  	2020. 
  	
 	\bibitem[Mannam+ 2019]{mannam2019}
  %	Pragna Mannam, Alexander Volkov, Jr., Robert Paolini, Gregory Chirikijan, Matthew T. Mason,
  	P. Mannam, A. Volkov, Jr., R. Paolini, G. Chirikijan, M. T. Mason,
  	``Sensorless Pose Determination Using Randomized Action Sequences'',
  	 {\it Entropy}, Vol.~21, No.~2, 154, 
  	2019.
  	
  	\bibitem[Akella+ 2000]{akella2000}
  	S. Akella, W. H. Huang, K. M. Lynch, M. T. Mason,
  	``Parts Feeding on a Conveyor with a One Joint Robot'',
  	 {\it Algorithmica},
  	 Vol.~26,
  	 pp.~313--344,
  	2000.
  	
  	\bibitem[Udhayakumar+ 2021]{udhayakumar2021}
  	S. Udhayakumar, A. Mohan, J. Gowthamachandran,  R. Prakash, P. Shanmugam,
  	``Development of Visionless Flexible Part Feeder for Handling Shock Absorbers'',
  	 Materials, Design, and Manufacturing for Sustainable Environment, Springer Singapole, 
  	 pp.~141--154,
  	2021.  	
  	
\bibitem[上久木田 2022]{kamikukita2022}
上久木田 治毅:
``センサレス in-hand ケージングマニピュレーションに基づく汎用パーツフィーダの開発'', 
横浜国立大学理工学部 機械・材料・海洋系学科 機械工学EP, 卒業論文, 2022.
  	
\bibitem[浅村 2013]{asamura2013} 
浅村 知洋:
``ロボットハンドのためのIn-hand ケージングマニピュレーション'', 
横浜国立大学大学院工学府 システム統合工学専攻, 修士論文, 2013.

  	\bibitem[LaValle+ 2001]{lavalle2001}
  	S. M. LaValle, J. J. Kuffner, 
  	``Rapidly-exploring Random Tree: Progress and Prospects'', 
  	{\it Algorithmic and Computational Robotics: New Directions 2000 WAFR}, 
  	in B. R. Donald, K. M. Lynch, and D. Rus, editors, 
  	pp.~293--308, A K Peters, 2001.
  	
  	\bibitem[Ester+ 1996]{ester1996}
  	M. Ester, H. Kriegel, J. Sander, X. Xu, 
  	``A Density-Based Algorithm for Discovering Clusters'', 
  	{\it Proceeding of the 2nd ACMSIGKDD}, 
  	pp.~226--231, 1996.
  	
  	\bibitem[Kuffner+ 2000]{kuffner2000}
%  	Walter G. Bircher, Andrew S. Morgan, Kaiyu Hang, Aaron M. Dollar,
	J. J. Kuffner, S. M. LaValle, 
	``RRT-connect: An Efficient Approach to Single-Query Path Planning'',
	{\it Proceedings 2000 ICRA. Millennium Conference. IEEE International Conference on Robotics and Automation. Symposia Proceedings (Cat. No.00CH37065)}, 
	 Vol.~2, pp.~995--1001, 2000.
  	
\end{thebibliography}

% 白魔術
\expandafter\ifx\csname ifdraft\endcsname\relax
    \end{document}
\fi
